---
title: "Example analysis of colony formation assay with kinase inhibitors"
author: "Author: Jessie A. van Buggenum"
output:
  html_notebook: 
    code_folding: show
    depth: 3
    fig_height: 2.25
    fig_width: 3
    number_sections: yes
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r functions and packages dependency, message=FALSE, warning=FALSE}
library(plyr)
library(data.table)
library(ggplot2)
library(ggthemes)
library(tidyr)
library(ggExtra)
library("RColorBrewer")
library(pheatmap)
library(dplyr)
library(ggrepel)
## Function to create summary table with mean, sd (and other calculations if added)

summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm),
          CV = sd     (xx[[col]], na.rm=na.rm) / mean   (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    #datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
    

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}


fancy_scientific <- function(l) {
  # turn in to character string in scientific notation
  l <- format(l, scientific = TRUE)
  # quote the part before the exponent to keep all the digits
  l <- gsub("^(.*)e", "'\\1'e", l)
  # turn the 'e+' into plotmath format
  # remove + after exponent, if exists. E.g.: (3x10^+2 -> 3x10^2) 
  l <- gsub("e\\+","e",l)
  # convert 1x10^ or 1.000x10^ -> 10^ 
  l <- gsub("\\'1[\\.0]*\\'\\%\\*\\%", "", l)
  l <- gsub("e", "%*%10^", l)
  # return this as an expression
  parse(text=l)
}
```

# Import data

```{r}
#mydata <- fread(file.choose(new = FALSE))  #ColoniesDraq5.csv

#colony_counts_perwell <- fread(file.choose(new = FALSE)) #Grid_6wells.csv

#image_ID_annotation <- fread(file.choose(new = FALSE)) #annotation_cellprofilerresults.csv

```


# Annotate data tables

```{r}
# rename duplicated column name
column_names <- colnames(mydata)
column_names[6] <- "Metadata_Image_ID_duplicated"
colnames(mydata) <- column_names

# rename column name image_ID_annotation
column_names_image_ID_mydata <- colnames(image_ID_annotation)
column_names_image_ID_mydata
column_names_image_ID_mydata[2] <- "Parent_Grid_6wells"
image_ID_annotation_mydata <- image_ID_annotation
colnames(image_ID_annotation_mydata) <- column_names_image_ID_mydata
# Add to mydata compound names
mydata <- tbl_df(mydata) %>%
  select(-Metadata_Image_ID_duplicated) %>%
  left_join(image_ID_annotation_mydata) 
#%>%   filter(!is.na(Compound))

# rename duplicated column name
column_names_2 <- colnames(colony_counts_perwell)
column_names_2[6] <- "Metadata_Image_ID_duplicated"
colnames(colony_counts_perwell) <- column_names_2

# Add to colony_counts tbl annotation
colony_counts_perwell <- colony_counts_perwell %>%
  left_join(image_ID_annotation)

```


```{r}
mydata <- mydata %>%
  mutate(IntegratedIntensity_TGM1_overDraq5 = Intensity_IntegratedIntensity_TGM1Corr/Intensity_IntegratedIntensity_Draq5Corr)

```

# Number of Colonies


```{r}
# Calculate mean and se colony counts per treatment
colony_counts_mean <- summarySE(data = colony_counts_perwell, measurevar = "Children_ColoniesDraq5_Count", groupvars = c("Compound","Target_Concentration") )

colony_counts_mean <- colony_counts_mean %>%
  filter(Compound != "Mock")

compounds <- unique(colony_counts_mean$Compound)

```


```{r, fig.width=3.6, fig.height=3}
for (compound in compounds){

plot <- 
  ggplot(subset(colony_counts_mean, Compound == compound), aes(x=Target_Concentration, y=mean)) + 
  geom_bar(stat = "identity", fill="grey", color="black", width = 0.8) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  xlab("") +
  ylab("# colonies") +
  ylim(c(0,300))+
  theme_few()  + 
  theme(axis.text.x = element_text(angle = 90,  hjust=1, vjus=0.5, size = 8), 
        axis.text.y = element_text(size = 8,  vjus=0.2), 
        axis.title = element_text(size=8))
#ggsave(filename = paste0("plots_r_processing/bar_number_of_colonies_",compound,"_2.pdf"), width = 3.6, height = 3)  
print(plot)
  
}

```

# Colony Area


```{r}

colony_Area_mean <- summarySE(data = mydata, measurevar = "AreaShape_Area", groupvars = c("Compound","Target_Concentration") )

colony_Area_mean <- colony_Area_mean %>%
  filter(Compound != "Mock")

```


```{r, fig.width=3.5, fig.height=3}
for (compound in compounds){

plot <- 
  ggplot(subset(colony_Area_mean, Compound == compound), aes(x=Target_Concentration, y=mean)) + 
  geom_bar(stat = "identity", fill="grey", color="black", width = 0.8) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  xlab("") +
  ylab("Colony Area") +
  #ylim(c(0,250))+
  theme_few()  + 
  theme(axis.text.x = element_text(angle = 90,  hjust=1, vjus=0.5, size = 8), axis.text.y = element_text(size = 8,  vjus=0.2), axis.title = element_text(size=8)) 

#ggsave(filename = paste0("plots_r_processing/bar_colony_area_",compound,"_2.pdf"), width = 3.5, height = 3)  
print(plot)
  
}

```


# Clone types {.tabset}


## Median radius to define subtypes of 


```{r, fig.width=6, fig.height=4}
ggplot(mydata, aes(fill=Target_Concentration, x=AreaShape_MedianRadius))+
  geom_density(kernel = "gaussian",adjust = 1/3, alpha = 0.1)+
  scale_fill_grey()+
  theme_few() + 
  theme(axis.text.x = element_text(angle = 0,  hjust=0.5), strip.text.x = element_text(size = 8), legend.position="none", legend.text = element_text(size=6)) +
  scale_x_log10()+
  geom_vline(xintercept = 1.2) +
  annotate("text", x = 1.12, y = 65, label = "Small < 1.2")+
  geom_vline(xintercept = 1.65) +
  annotate("text", x = 2, y = 65, label = "large > 1.65")

```

```{r}
ggsave(filename = "plots_r_processing/radius_density_cutoffs_2.pdf", width = 6, height = 4)
```

```{r}
mydata <- mydata %>%
  mutate(colony_type = ifelse(AreaShape_MedianRadius < 1.2, "small", "medium")) %>%
  mutate(colony_type = ifelse(AreaShape_MedianRadius > 1.65, "large", colony_type)) 

mydata_colony_types <- mydata %>%
  group_by(Compound, colony_type, Target_Concentration) %>%
  summarise(colony_type_frequency = n()) %>%
  select(Compound, colony_type, colony_type_frequency, Target_Concentration)  %>%
  ungroup()%>%
  filter(Compound != "Mock")

```


```{r}
df <- mydata_colony_types 

# Get the levels for type in the required order
df = arrange(df, Target_Concentration, sort(Target_Concentration, decreasing=FALSE))

# Calculate the percentages
df = ddply(df, .(Target_Concentration), transform, percent = colony_type_frequency/sum(colony_type_frequency) * 100)


# Format the labels and calculate their positions
df = ddply(df, .(Target_Concentration), transform, pos = (cumsum(colony_type_frequency) - 0.5 * colony_type_frequency))
df$label = paste0(sprintf("%.0f", df$percent), "%")
```

```{r, fig.width=4, fig.height=3.3}
for (compound in compounds){

plot <- 
  ggplot(subset(df, Compound == compound), aes(x = Target_Concentration, y = colony_type_frequency, fill = colony_type)) +
  scale_fill_grey()+
   geom_bar(position = position_fill(), stat = "identity", width = .7) +
     geom_text(aes(label = label), position = position_fill(vjust = 0.5), size = 2) +
   theme_few() + 
  theme(axis.text.x = element_text(hjust=0.5, vjus=0.5, size = 8), axis.text.y = element_text(size = 8,  vjus=0.2), axis.title = element_text(size=8), legend.position = "top") +
  coord_flip()

#ggsave(filename = paste0("plots_r_processing/bar_colony_types_percentages_",compound,"_2.pdf"), width = 4, height = 3.3)  
print(plot)
  
}

```


# Differentiation marker (TGM1/Draq5)

```{r}
mydata_TGM1_over_Draq5 <- mydata %>%
  mutate(IntegratedIntensity_TGM1_overDraq5 = Intensity_IntegratedIntensity_TGM1Corr/Intensity_IntegratedIntensity_Draq5Corr)

colony_IntegratedIntensity_TGM1_overDraq5_mean <- summarySE(data = mydata_TGM1_over_Draq5, measurevar = "IntegratedIntensity_TGM1_overDraq5",  groupvars = c("Compound","Target_Concentration")) %>%
  filter(Compound != "mock") 

```


```{r, fig.width=3.6, fig.height=3}
for (compound in compounds){

plot <- 
  ggplot(subset(colony_IntegratedIntensity_TGM1_overDraq5_mean, Compound == compound), aes(x=Target_Concentration, y=mean)) + 
  geom_bar(stat = "identity", fill="grey", color="black", width = 0.8) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  xlab("") +
  ylab("TGM1/Draq5") +
  #ylim(c(0,300))+
  theme_few()  + 
  theme(axis.text.x = element_text(angle = 90,  hjust=1, vjus=0.5, size = 8), 
        axis.text.y = element_text(size = 8,  vjus=0.2), 
        axis.title = element_text(size=8))
#ggsave(filename = paste0("plots_r_processing/bar_TGM1_overDRaq5_",compound,"_2.pdf"), width = 3.6, height = 3)  
print(plot)
  
}

```


# Dose response curves

## Description

Installed the drc package for dose-response analysis 

```{r}
library(drc)
library(sandwich)
library(lmtest)
library(multcomp)
```

```{r}
citation('drc')
```


Used the code from the supplements for Continuous response: one dose-response curve

Calculated:  
- Model parameters  
- Robust robust standard errors  
- Estimating effective doses ED50

## Colony number {.tabset}

### ggplots of colony number

Plots below show that 4 out of 5 compounds have no colonies at concentration=20. 

```{r, fig.width=3, fig.height=2}

# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
colony_counts_perwell$Concentration0 <- colony_counts_perwell$Concentration
colony_counts_perwell$Concentration0[colony_counts_perwell$Concentration0 == 0] <- 0.005

for (compound in compounds){
compound.LL.4 <- drm(Children_ColoniesDraq5_Count ~ Concentration, data = subset(colony_counts_perwell, Compound == compound ), fct = LL.5())

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(30), length=100)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]

# plotting the curve
ggplot(subset(colony_counts_perwell, Compound == compound ), aes(x = Concentration0, y = Children_ColoniesDraq5_Count)) +
geom_point(shape = 1, size=2) +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("Colony Number") +
  ylim(c(0,NA))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4,20),
                   label = c(0,0.032, 0.16, 0.8, 4,20))+
theme_few()
print(last_plot())
}



```
### without concentration 20 uM

```{r, fig.width=3, fig.height=2}


# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
colony_counts_perwell$Concentration0 <- colony_counts_perwell$Concentration
colony_counts_perwell$Concentration0[colony_counts_perwell$Concentration0 == 0] <- 0.005


for (compound in compounds){

compound.LL.4 <- drm(Children_ColoniesDraq5_Count ~ Concentration, data = subset(colony_counts_perwell, Compound == compound & Concentration != 20), fct = LL.5())

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(5), length=100)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]


# plotting the curve
ggplot(subset(colony_counts_perwell, Compound == compound & Concentration != 20), aes(x = Concentration0, y = Children_ColoniesDraq5_Count)) +
geom_point(shape = 1, size=2) +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("Colony Number") +
  ylim(c(0,NA))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4),
                   label = c(0,0.032, 0.16, 0.8, 4))+
theme_few()

print(last_plot())


}




```

## Colony Area {.tabset}

Because most compounds have no colonies at concentration 20, and thus have no calculated parameters like colony area, I excluded this point for the parameter models.

```{r, fig.width=2.8, fig.height=3}

tbl_mean_perwell_parameterx <- summarySE(data = subset(mydata_TGM1_over_Draq5,Concentration != 20), measurevar = "AreaShape_Area" ,  groupvars = c("Compound","Concentration","replicate")) %>%
  filter(Compound != "mock") 
  
for (compound in compounds){

compound.LL.4 <- drm(mean ~ Concentration, data = subset(tbl_mean_perwell_parameterx, Compound == compound), fct = LL.5())

#print(summary(compound.LL.4))
#print(coeftest(compound.LL.4, vcov = sandwich))
#print(ED(compound.LL.4, c(5, 10, 50), interval = "delta"))

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(5), length=50)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]

# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
tbl_mean_perwell_parameterx$Concentration0 <- tbl_mean_perwell_parameterx$Concentration
tbl_mean_perwell_parameterx$Concentration0[tbl_mean_perwell_parameterx$Concentration0 == 0] <- 0.005

# plotting the curve
ggplot(subset(tbl_mean_perwell_parameterx, Compound == compound), aes(x = Concentration0, y = mean)) +
geom_point(shape = 1, size=2.5, color="darkgrey") +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("AreaShape_Area") +
  ylim(c(0,220))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4),
                   label = c(0,0.032, 0.16, 0.8, 4))+
theme_few()
#ggsave(filename = paste0("plots_r_processing/line_colony_area_",compound,"_2.svg"), width = 2.8, height = 3)  
print(last_plot())

}

```

PF4708371 with all 5 concentrations


```{r, fig.width=2.8, fig.height=3}
tbl_mean_perwell_harmine <- summarySE(data = subset(mydata_TGM1_over_Draq5), measurevar = "AreaShape_Area" ,  groupvars = c("Compound","Concentration","replicate")) %>%
  filter(Compound != "mock") 

for (compound in compounds[4]){

compound.LL.4 <- drm(mean ~ Concentration, data = subset(tbl_mean_perwell_harmine, Compound == compound), fct = LL.5())

#print(summary(compound.LL.4))
#print(coeftest(compound.LL.4, vcov = sandwich))
#print(ED(compound.LL.4, c(5, 10, 50), interval = "delta"))

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(30), length=50)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]

# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
tbl_mean_perwell_harmine$Concentration0 <- tbl_mean_perwell_harmine$Concentration
tbl_mean_perwell_harmine$Concentration0[tbl_mean_perwell_harmine$Concentration0 == 0] <- 0.005

# plotting the curve
ggplot(subset(tbl_mean_perwell_harmine, Compound == compound), aes(x = Concentration0, y = mean)) +
geom_point(shape = 1, size=2.5, color= "darkgrey") +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("AreaShape_Area") +
  ylim(c(0,220))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4,20),
                   label = c(0,0.032, 0.16, 0.8, 4,20))+
theme_few()
ggsave(filename = paste0("plots_r_processing/line_colony_area_PF4708371_extra20uM","_2.svg"), width = 2.8, height = 3)  
print(last_plot())

}

```

## Integrated Intensity TGM1/Draq5


```{r, fig.width=2.8, fig.height=3}

tbl_mean_perwell_parameterx <- summarySE(data = subset(mydata_TGM1_over_Draq5,Concentration != 20), measurevar = "IntegratedIntensity_TGM1_overDraq5" ,  groupvars = c("Compound","Concentration","replicate")) %>%
  filter(Compound != "mock") 
  
for (compound in compounds){

compound.LL.4 <- drm(mean ~ Concentration, data = subset(tbl_mean_perwell_parameterx, Compound == compound), fct = LL.5())

#print(summary(compound.LL.4))
#print(coeftest(compound.LL.4, vcov = sandwich))
#print(ED(compound.LL.4, c(5, 10, 50), interval = "delta"))

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(5), length=50)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]

# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
tbl_mean_perwell_parameterx$Concentration0 <- tbl_mean_perwell_parameterx$Concentration
tbl_mean_perwell_parameterx$Concentration0[tbl_mean_perwell_parameterx$Concentration0 == 0] <- 0.005

# plotting the curve
ggplot(subset(tbl_mean_perwell_parameterx, Compound == compound), aes(x = Concentration0, y = mean)) +
geom_point(shape = 1, size=2.5, color="darkgrey") +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("IntegratedIntensity_TGM1_overDraq5") +
  ylim(c(0,1.7))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4),
                   label = c(0,0.032, 0.16, 0.8, 4))+
theme_few()
ggsave(filename = paste0("plots_r_processing/line_II_TGM1overDraq5_",compound,"_2.svg"), width = 2.8, height = 3) 
print(last_plot())

}
```

PF4708371 with 20 uM

NOTE that LL.4() is used (and not LL.5() as with other compounds )

```{r, fig.width=3, fig.height=2.5}

tbl_mean_perwell_parameterx <- summarySE(data = subset(mydata_TGM1_over_Draq5), measurevar = "IntegratedIntensity_TGM1_overDraq5" ,  groupvars = c("Compound","Concentration","replicate")) %>%
  filter(Compound != "mock") 
  
for (compound in compounds[4]){

compound.LL.4 <- drm(mean ~ Concentration, data = subset(tbl_mean_perwell_parameterx, Compound == compound), fct = LL.4())

#print(summary(compound.LL.4))
#print(coeftest(compound.LL.4, vcov = sandwich))
#print(ED(compound.LL.4, c(5, 10, 50), interval = "delta"))

# new dose levels as support for the line
newdata <- expand.grid(Concentration=exp(seq(log(0.005), log(30), length=100)))
#newdata <- expand.grid(Concentration=c(0.005,0.032, 0.16, 0.8, 4, 20))
# predictions and confidence intervals
pm <- predict(compound.LL.4, newdata=newdata, interval="confidence")
# new data with predictions
newdata$p <- pm[,1]
newdata$pmin <- pm[,2]
newdata$pmax <- pm[,3]

# need to shift conc == 0 a bit up, otherwise there are problems with coord_trans
tbl_mean_perwell_parameterx$Concentration0 <- tbl_mean_perwell_parameterx$Concentration
tbl_mean_perwell_parameterx$Concentration0[tbl_mean_perwell_parameterx$Concentration0 == 0] <- 0.005

# plotting the curve
ggplot(subset(tbl_mean_perwell_parameterx, Compound == compound), aes(x = Concentration0, y = mean)) +
geom_point(shape = 1, size=2.5, color = "darkgrey") +
#geom_ribbon(data=newdata, aes(x=Concentration, y=p, ymin=pmin, ymax=pmax), alpha=0.2) +
geom_line(data=newdata, aes(x=Concentration, y=p)) +
coord_trans(x="log") +
xlab(paste0("Concentration ",compound, " (uM)")) + ylab("IntegratedIntensity_TGM1_overDraq5") +
  ylim(c(0,1.7))+
scale_x_continuous(breaks = c(0.005,0.032, 0.16, 0.8, 4,20),
                   label = c(0,0.032, 0.16, 0.8, 4,20))+
theme_few()
ggsave(filename = paste0("plots_r_processing/line_II_TGM1overDraq5_PF4708371_with20uM","_2.svg"), width = 2.8, height = 3) 
print(last_plot())

}
```
